---
author: "Carl Boettiger"
institute: "UC Berkeley"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "solarized-light.css"]
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: "solarized-light"
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(#dev.args=list(bg="transparent"), 
                      echo = FALSE, 
                      message=FALSE, 
                      warning=FALSE,
                      fig.width=11, 
                      fig.height=6.5, 
                      cache = TRUE)

library(tidyverse)
library(ggthemes)
library(magick)
theme_set(theme_solarized(base_size=16))
scale_colour_discrete <- function(...) scale_colour_solarized()
scale_fill_discrete <- function(...) scale_fill_solarized()
pal <- solarized_pal()(6)

txtcolor <- "#586e75"


library(patchwork)
ggimage <- function(path, transparent = FALSE){
  img <- magick::image_read(path)
  if(transparent)  img <- magick::image_transparent(img, "white")
  ggplot2::ggplot() + 
  ggplot2::annotation_raster(img, 
                    xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
    theme(axis.line = element_blank(), 
          panel.background = element_blank(),
          axis.ticks = element_blank(), 
          axis.text = element_blank(), 
          axis.title = element_blank())
  
}

ggblank <- function() ggplot() + geom_blank() + 
  theme(axis.line = element_blank(), panel.background = element_blank())

```

layout: true
background-color: #fdf6e3
class: center, top

---

# My talk title here

## Subtitle H2

### H3

#### H4

##### H5 

Text with *emphasis*

<div class="my-footer">

<a href="https://carlboettiger.info"> `r icon::fa("user")` Carl Boettiger</a> | 
<a href="https://berkeley.edu"> `r icon::fa("briefcase")` UC Berkeley</a> | 
<a href="https://twitter.com/cboettig"> `r icon::fa("twitter")` @cboettig</a>

</div>

---

# First Slide

.pull-left[

- bulleted list
- the bullets are invisible
- that's nicer for centered text

]
.pull-right[

```{r fig.width=6, fig.height=4}
ggplot(mtcars, aes(cyl, mpg, fill=as.factor(cyl))) +
  geom_bar(stat="identity", show.legend = FALSE) + 
  ggtitle("Not mtcars again!")
```
]



---

# Acknowledgements

.pull-left[

## Group

```{r fig.width=6, fig.height=6}
(ggimage("../image-library/people/milad.png") +
ggimage("../image-library/people/millie.png")) / 
(ggimage("../image-library/people/marcus.jpg") + plot_spacer())
```




]
.pull-right[


## Funding

```{r fig.width=12, fig.height=6}
(ggimage("../image-library/sponsors/nsf.png")  +     
 ggimage("../image-library/sponsors/bids.png", TRUE) +
 ggimage("../image-library/sponsors/jetstream-logo.svg", TRUE)
)  /     
(ggimage("../image-library/sponsors/hellman.png")  +    
 ggimage("../image-library/sponsors/berkeley.png")
)

  
```


### Image Credits

```{r fig.width=10, fig.height=2}
plot_spacer() + 
  ggimage("../image-library/people/allison_horst_artist.jpg") + xlab("Allison Horst") + 
  ggimage("../image-library/sponsors/royalsociety.jpg") + ylab("Image Credits")  +
  ggimage("../image-library/sponsors/noaa.png", TRUE) +
  plot_spacer() + plot_layout(ncol=5)

```

]